How is the Brazilian Amazon constructed as a problem at different levels? Amazonian

### 2022-02-11 20220210_Draft.Rmd
#dictionarycorrection

sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|defesa|exercito|donoo|internacionalizar|fronteira")

>>>>

sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|defesa|exercito|dono|internacionalizar|fronteira")
